Trends in Preventive Care Practices among US Adults with Diabetes, 2008-2020 

### 2022-12-22 scripts/manuscript/manuscript_draft.qmd
Transitioning to server

@@

The data we used comes from the full-year consolidated file from MEPS for the 12 year time span. Our analysis is adjusted for the complex survey design

@@

```{r}
tar_load(age_adjusted_preventive)
age_adjusted_preventive %>% 
  filter(label == 'Three preventive practices followed') %>% 
  mutate(age_adjusted_prop = age_adjusted_prop * 100) %>% 
  pivot_wider(
    id_cols = c(stratifier, variable, label, strata),
    names_from = year,
    values_from = age_adjusted_prop
  ) %>% 
  group_by(stratifier, strata) %>%
  select(stratifier, label, `2008`:`2020`) %>%
  gt() %>% 
  fmt_number(columns = `2008`:`2020`, decimals = 1) %>% 
  gtsave('preventive_practices.docx')
```

>>>>

`%!in%` <- Negate(`%in%`)

@@

The data we used comes from the full-year consolidated file from MEPS for the 12 year time span. Our analysis is adjusted for the complex survey design, including clustering and stratification.

@@

```{r}
tar_load(age_adjusted_preventive)
preventive_practice_table <- age_adjusted_preventive %>% 
  filter(label == 'At least three preventive practices followed') %>% 
  mutate(age_adjusted_prop = age_adjusted_prop * 100) %>% 
  pivot_wider(
    id_cols = c(stratifier, variable, label, strata),
    names_from = year,
    values_from = age_adjusted_prop
  ) %>% 
  filter(strata %!in% c('Not available', 'Other Race/Not Hispanic')) %>% 
  mutate(stratifier = factor(stratifier,
                             c('overall', 'age', 'sex', 'race', 'edu', 'insurance', 'poverty')),
         strata = case_when(strata == 'stat_0' ~ '-', 
                            strata == 'Greater than HS' ~ 'Greater than high school',
                            TRUE ~ strata)) %>% 
  mutate(strata = as.factor(strata)) %>% 
  mutate(stratifier = recode_factor(
    stratifier,
    overall = 'Overall',
    age = 'Age',
    sex = 'Sex',
    race = 'Race/Ethnicity',
    edu = 'Highest degree earned',
    insurance = 'Insurance coverage',
    poverty = 'Poverty level'
  )) %>% 
  group_by(stratifier) %>%
  select(stratifier, strata, `2008`:`2020`) %>%
  gt() %>% 
  fmt_number(columns = `2008`:`2020`, decimals = 1)
preventive_practice_table$`_data` <- preventive_practice_table$`_data`[c(1:18, 20, 19, 21), ]
preventive_practice_table %>% 
  gtsave('preventive_practices.docx')
```

```{r}

preventive_practice_table <- age_adjusted_preventive %>% 
  filter(label == 'At least three preventive practices followed') %>% 
  mutate(age_adjusted_prop = age_adjusted_prop * 100) %>% 
  pivot_wider(
    id_cols = c(stratifier, variable, label, strata),
    names_from = year,
    values_from = age_adjusted_prop
  ) %>% 
  filter(strata %!in% c('Not available', 'Other Race/Not Hispanic')) %>% 
  mutate(stratifier = factor(stratifier,
                             c('overall', 'age', 'sex', 'race', 'edu', 'insurance', 'poverty')),
         strata = case_when(strata == 'stat_0' ~ '-', 
                            strata == 'Greater than HS' ~ 'Greater than high school',
                            TRUE ~ strata)) %>% 
  mutate(strata = as.factor(strata)) %>% 
  mutate(stratifier = recode_factor(
    stratifier,
    overall = 'Overall',
    age = 'Age',
    sex = 'Sex',
    race = 'Race/Ethnicity',
    edu = 'Highest degree earned',
    insurance = 'Insurance coverage',
    poverty = 'Poverty level'
  )) %>% 
  group_by(stratifier) %>%
  select(stratifier, strata, `2008`:`2020`) %>%
  gt() %>% 
  fmt_number(columns = `2008`:`2020`, decimals = 1)
preventive_practice_table$`_data` <- preventive_practice_table$`_data`[c(1:18, 20, 19, 21), ]
preventive_practice_table %>% 
  gtsave('preventive_practices.docx')
```
